
The goal is to drive the system to an optimal periodic trajectory, so the first step is to generate this trajectory. This trajectory is 
submitted to restrictions imposed by the dynamic of the system and also switching time restrictions.

We must establish a trajectory that yields the optimal time sequence $T^\infty$, the modes sequence $\Omega^\infty$, and its 
length $s^\infty (1 < s^\infty < s_{max})$. To reduce the oscillations around a desired operation point, we choose an integral 
quadratic criterion centered on the average reference value $\bar{x}^\infty$:

\begin{equation}
    J(\tau^{\infty} ,\Omega^{\infty} ,s^{\infty}) = \min_{\tau, \Omega, s} \int_0^{T_p} \Big[x(t) - \bar{x}^{\infty}\Big]^T Q \Big[x(t) - \bar{x}^{\infty}\Big] dt
\end{equation}

\noindent
where $Q=Q^T>0$ and $T_p$ is the period of the cycle.

Since the trajectory is cyclic we can impose the constraint:

\begin{equation}
    x(0) = x(T_p)
\end{equation}



\section{Optimization}

    The way we solve this periodic trajectory is, first we create 
    a list of modes for the system, where each mode has its unique dynamics, 
    defined by the matrices A, B, C, and D.  
    Then we set up a sequence of which modes to run in the optimization and 
    establish constraints for the maximum period of the cycle, along with constraints 
    for the minimum and maximum time allowed between mode switches
    Utilizing FMINCON, an optimization is run that generates the switching times, 
    respecting the imposed constraints, and evaluating them through a specified cost function.

    The cost function takes the time and the sequence of modes, and computes the 
    initial condition of the states to that the result is a cyclic trajectory. 
    Subsequently, the integral of the trajectory around the average reference value $\
    bar{x}^\infty$ is computed.  This formulation of the cost function 
    finds a solution that satisfies both the dynamical constraints of the system and 
    the desired properties of the resulting trajectory.


    \purple{
        The way we solve this is by:

        \begin{itemize}

            \item create a list of the modes for the system, each mode with its own dynamics (matrix A, B, C, D).
            
            \item create a vector with the sequence of modes to run on the optimization.
            
            \item establishes the constraints of the maximum period for the cycle and also for minimum and maximum time between switches.
            
            \item runs an optimization using FMINCON that generates the switches with the constraints and evaluates them with the cost function. 
            
            \item the cost function receives the generated switching time and the sequence of modes. 
            
            \item then computes the initial condition of the states so that the result is a cyclic trajectory. 
            
            \item then it computes the integral of the trajectory around the average reference value $\bar{x}^\infty$.

        \end{itemize}
    }

\section{Calculating $x_0$}


    A condiçăo inicial é determinada de forma que o ultimo ponto é coincidente com o primeiro ponto (dada a sequencia de modos e instantes de chaveamento)

        \begin{equation}
            x(0) = \Big(I - F_N F_{N-1} \ldots F_1\Big)^{-1} c
        \end{equation}
        
        \begin{equation}
            c = F_N F_{N-1} \ldots F_2 G_1 u_1 + F_N F_{N-1} \ldots F_3 G_2 u_2 + \ldots + F_N G_{N-1} + G_N u_N
        \end{equation}

\input{Cap2/cap2_otim_get_x0}

\section{Application Examples}

\subsection{Variant Dynamic Circuit 1}

\subsection{Variant Dynamic Circuit 2}