\section{Motivation}

    \red{
        The dynamics of switched affine systems can be described by a state equation of the form 
        $\dot{x}(t) = A_{\sigma(t)} x(t) + b_{\sigma(t)}, t \in \mathbb{R}_+$. Where $x(t) \in \mathbb{R}^n$ is the state vector and $\sigma(t) \in \{1, 2, ..., N\}$ is the switching state, 
        which is associated to the matrix $A_{\sigma(t)} \in \mathbb{R}^{n \times n}$ and the 
        vector $b_{\sigma(t)} \in \mathbb{R}^{n}$ at each time $t$.
    }

    \purple{ 
        Some work have been done in controlling a system that can be expressed as a switched affine system. In \citeonline{zhu2020} the author proposes 
        controlling the switching time of the system submited to minimal dwell-time restriction between two consecutive switchings and apply his 
        work in a pneumatic artificial muscle system to satisfy the high-performacne requirements in a highly nonlinear nature system.

        \citeonline{sanchez2019} also investigates the problem of a switched affine system submited to dwell-time constraint, in this work he uses
        two different solutions using hybrid lyapunov theory control law and proposes two provied tuning knobs to separately adjust the swithing 
        frequency during transients and at the steady state in a silulated boost converter.

        \citeonline{{xu2022}} proposes a $H\infty$ control of limit cycle to increase the performance of the system by 
        controlling the trajetory to a desired limit cycle instead of a small neighborhood. He demonstrates the results in a numerical example
        and also in a practical example using a boost converter.
    }

    Most of the proposed controllers solve this type of problem by driving the system states to the neighborhood of the 
    target states and, in continuous=time switched affine systems, this means that the system will find stability in a periodic trajectory near 
    the target but, without further consideration of this resulting periodic trajetory, we can experience performance degradation in the system.

    The dynamics of switched affine systems can be described by a state equation of the form $t \in \mathbb{R}_+$
    where x(t) $\in \mathbb{R}^n$ is the state vector and $\sigma(t)$ $\in$ $\{1, 2, ..., N\}$ is the switching state, 
    which is associated to the matrix $A_{\sigma(t)} \in \mathbb{R}^{n \times n}$ and the vector $b_{\sigma(t)} \in \mathbb{R}^{n}$ 
    at each time $t$.

    
    % ok \red{introduzir sistemas chaveados afins e dificuldade de um sistema chaveado afim de conduzir a trajetoria para um ponto}

    The use of switched affine systems to solve problems in engineering can be seeing in fields like: biochemical reactions, where 
    \citeonline{reference_biochemical_reaction} uses switched affine systems to represent the moments of evolution in a generic biochemical 
    reaction network; urban traffic, where \citeonline{reference_urban_traffic_control} approaches the urban traffic control; power converters, 
    where \citeonline{benmiloud2018} also uses this approach and other areas where the behavior of the system can be described as a switched 
    affine system.

    There are some studies that forms the basis for the present work: 

    \citeonline{marcio2013} solved the problem for a particular class of affine systems. Here the controller drived the system to a 
    target state using MILP (Mixed-Integer Linear Programming) and the cyclic trajectory was a consequence of the states as the system 
    approached the target.

    \citeonline{patino2010predictive} defined the target trajectory using non linear programming and used this target trajectory in the predictive 
    control in terms of errors.

    \citeonline{matheus2018} proposed a solution with a controller law that drives the system to a target cyclic trajectory. 
    In this work, the problem is addressed in two stages: first, the problem is interpreted as a convex otimization where the author is able to 
    find a targed cyclic trajectory that minimizes a cost function associated with the system performance; then a second part that uses the 
    target trajectory as input and applies pertubation on the instants of switching of the control signal using predictive control. 
    
\section{Contributions of the present work}

    This present work proposes to expand the solution from \citeonline{}{matheus2018} and provide a broader solution that can be used for systems 
    that have their dynamics changing over time.

    In a system that can be represented by a switched affine system with the form 

    $ \dot{x}(t) = A_{\sigma(t)} x(t) + b_{\sigma(t)} $

    there are cases in which dynamic response of the system can changedepending on the operation mode. This can be represented in 
    switched affine systems with proper matrices $A_{\sigma(t)}$ and $b_{\sigma(t)}$ for each operation mode. With the current implementation
    of \citeonline{matheus2018} considering a invariant system during its operation, there is a need for expanding the solution so it can represent
    more systems and solve more engineering problems that can be expressed as switched affine systems.

\section{Outline of the remaining chapters}
    
    The remaining of this text is organized as follows. Chapter 2 describes the problem of finding a target periodic trajectory for the 
    given switched affine system. Chapter 3 proposes then a predictive control law that drives the system to the target cyclic trajectory. 
    Finally, chapter 4 brings some remarks and considerations of the work.