\chapter{Conclusion}

This work consists of extending the solution of controlling a switched affine system 
subjected to dwell-time constraints to control this class of systems also with changing 
dynamics at switching times. This allows the method to be used in more control problems 
and maintains the convenience of solving the control problem with quadratic programming 
convex optimization, which is a mature class of optimization problems.

To test the method, first, a double integrator system with fixed dynamics was implemented in session \ref{cap4_aplication_integrador}
to validate the new solution. The result shows that the system diverges when not in the cyclic trajectory without the MPC controller and 
the controller is capable of correcting the trajectory and eventually engaging with the target trajectory.

The application example in session \ref{cap4_applicaton_patino1} introduces a system with changing dynamics at each switching time. 
A cyclic trajectory was calculated in session \ref{cap2_application_patino1} to use as an input parameter to implement the control method.
In this example, the circuit has stable dynamics that converge to the cyclic trajectory. Using the MPC controller reduces the time to converge
as can be seen in the comparison of the trajectories.

The multilevel converter in session \ref{cap4_applicaton_patino2} is a circuit that 
introduces more complexity, there are more operation modes and even modes that are repeated
during the same cycle. The simulation without the MPC shows a trajectory that converges to a cyclic limit 
that is different than the target cyclic trajectory. With the use of the MPC controller, we see that the system 
is driven to the target trajectory. The limit cycle of this circuit is also changing with different initial conditions,
in a first analysis this could be due to a numerical error in the simulation given that the numbers for this example 
are very small and susceptible to float point precision errors, but more work is needed to explain this behavior.

\comentariopurple{
    colocar referencia extado aumentado
}

Future work will include the reimplementation of the linearization using augmented states, this approach seems to simplify
the process for getting a linear prediction equation for the cycle error and would add improvement to the current work.

Another important work to do on top of the current state is to implement a physical in-lab multilevel circuit and apply the 
control solution in an embedded environment, the majority of the references in the topic treated the problem in the simulation domain 
and a real application would enrich the work. Also on this topic of thinking in real applications, future work contemplates the
implementation in the simulation of the clock cycles, this means that the instants to switch the operation mode would be multiplies of the
computer time, in circuits with time constants that are very small like the multilevel converter example this would cause a rounding error
that would lead to perturbation being injected into the circuit.

We propose the time to finish the project to be in 3 semesters. The first one is to finish the theoretical dependencies and analysis  
on the digital domain of the work, the second is to implement the real circuit in-lab and the last is to wrap all results in the final work.